\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.1in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Mohammad Ishan Rayeen}} & Email : \href{mailto:ishan0445@gmail.com}{ishan0445@gmail.com}\\ Mobile : \href{tel:7000583795}{+91-7000583795} &
\end{tabular*}

%-----------CURRENT ROLE--------------
\section{Current Role}
I am working as a \textbf{Software Development Engineer} at \textbf{Apple India Pvt. Ltd}.\\
My current position is \textbf{Individual Contributor Tech 3} working in \textbf{Privacy and Compliance} space. \\



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {International Institute of Information Technology}{Hyderabad, India}
      {Master of Technology, Computer Science and Engineering, \textbf{2016-2018}}{CGPA: 08.50}
    \resumeSubheading
      {Gyan Ganga College of Technology}{Jabalpur, MP, India}
      {Bachelor of Engineering, Computer Science and Engineering, \textbf{2012-2016}}{CGPA: 08.06}
    \resumeSubheading
      {St.Aloysius Sen. Sec. School}{Jabalpur, MP, India}
      {Intermediate, CBSE, \textbf{2012}}{Percentage: 76.40\%}
    \resumeSubheading
      {St.Aloysius Sen. Sec. School}{Jabalpur, MP, India}
      {Matriculation, CBSE, \textbf{2010}}{Percentage: 77.90\%}
  \resumeSubHeadingListEnd 


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Apple India Pvt. Ltd}{Hyderabad, Telangana, India}
      {Individual Contributor Tech 3}{June, 2018 - Present}
        \resumeItemListStart
            \resumeItem{Privacy and Compliance}
            {\\
            Worked on end to end, development, deployment and testing of a distributed anonymization engine. \\
            This application is used by various teams to anonymize any personal identifiable information (such as email and user id) entering the Business Intelligence space.\\
            
            \textbf{Technology stack:} \\
            Java, Scala, Docker, Kubernetes, AWS, Cassandra, Oracle, Kafka.
            }
        
        \resumeItemListEnd
        
    
    
    \resumeSubheading
      {Thyrocare Technologies Limited}{Navi Mumbai, Maharashtra, India}
      {Summer Internship}{May, 2017}
      \resumeItemListStart
        \resumeItem{Android Developer}
          {Developed 3 applications:
          \resumeItemListStart
            \resumeItem{Blood Technicians (BTech App)}
            {\\
            This app is used by the blood technicians(BTech), it displays the orders they are getting, location, amount and the tests they have to perform.}
            \resumeItem{Order Management System (OMS)}
            {\\
            This app is used by the operators, they can view all orders, accept/reject orders, generate new orders or track orders.}
            \resumeItem{Blood Technician Management System (BMS)}
            {\\
            This app is also used by the operators, they transfers orders to the BTechs that are idle, they can get a list of BTechs that are offline, standby, etc.}
          \resumeItemListEnd
          }
      \resumeItemListEnd


\section{Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: \\ 
     C++, C, Java, Python, Shell Scripting.}
    }
    \item{
     \textbf{Web Development}{: \\
     HTML, CSS, Javascript, JQuery, NodeJS, MongoDB.}
    }
    \item{
     \textbf{Operating Systems}{: \\
     Unix, Linux, MacOS, Windows, Android.}
    }
 \resumeSubHeadingListEnd


\end{document}